Short-term hourly forecasting for care services

### 2021-10-07 paper/paper.Rmd

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
library(ggridges)
library(hrbrthemes)
library(ggthemes)
library(scales)
library(ggtext)
library(extrafont)
```

@@

Let $y_t$ be the number of attendances in time period $t$ and indicate with $F_t(y_t)$ its predictive cumulative probability distribution. In a distributional regression context, $F_t(y_t)$ is modelled via a parametric model, $F(y_t|\bm \theta_t)$, where $\bm \theta_t$ is an $m$-dimensional vector of parameters. In a GAMLSS framework @Rigby2005 the elements $j=1,...,m$ of $\bm \theta_t$ are modelled via

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
library(ggplot2)
library(data.table)
library(RColorBrewer)
library(ggridges)
library(hrbrthemes)
library(ggthemes)
library(scales)
library(ggtext)
library(extrafont)
```

@@

If we assume that our predictive distribution follows a given parametric distribution, the forecasting task becomes ones of predicting the future values of that distribution's parameters. Generalised Additive Models for Location, Scale and Shape (GAMLSS) are distributional regression models where the parameters of the assumed distribution may be modelled as additive functions of explanatory variables. This provides a powerful and flexible framework for probabilistic forecasting, provided that a suitable distribution and additive structures can be found. In practice, this means experimenting with various distributions and evaluating their suitability using available training data.
Let $y_t$ be the number of attendances in time period $t$ and indicate with $F_t(y_t)$ its predictive cumulative probability distribution. In a distributional regression context, $F_t(y_t)$ is modelled via a parametric model, $F(y_t|\bm \theta_t)$, where $\bm \theta_t$ is an $m$-dimensional vector of parameters. In a GAMLSS framework @Rigby2005 the elements $j=1,...,m$ of $\bm \theta_t$ are modelled via
